Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-05 Paper/paper.tex
worked on introduction

%The Internet is Dynamic and growing
The Autonomous Systems layer of the Internet has grown and changed dramatically over its history.
In the early 2000s, there were around 10,000 ASes connected to the global AS graph. Today there are
over 60,000 of these ASes. The locations and relationships of these ASes determine how many chokepoints
of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion of the AS graph suggests a dynamic system with behavior that is important for
understanding things like path robustness, AS hierarchies, and the potential for governments to control
information as it flows in and out of their borders. It is certain that structrural qualities of national
AS graphs have evolved differently from nation to nation, whether that be due to economic decision making, infrastructural
necessities, or efforts to build a powerful censorship and surveillance network.

%Current Events
\par
The Internet has been used as a tool for the citizens of authoritarian nations to voice opinions,
organize revolutionary movements, and connect with other nations' governments and citizens
to seek aid. Much of the organization, revolutionary momentum, and broadcasting
of happenings during the Arab Spring can be attributed to social media communications
through the Internet \cite{arabspring}. Because of this potential, national governments may
take interest in maximizing their ability to control the flow of information on the Internet.
%Censorship and Surveillance are growing phenomena
\par
Internet censorship and surveillance have become profound social and technical issues facing the world. The portion of the
global population that uses the Internet has increased substantially in recent years. According to the International Telecommunication Union,
the number of individual users of the Internet has increased from 1.024 million in 2005 to 3.578 million in 2017 \cite{itu}. Of the Internet
population, a majority of them are subject to some lack of Internet freedom. The 2017 Freedom on the Net report from freedom house reports that
64\% of Internet users belong to a nation with Internet that is not free or partly free \cite{FOTN}. It is evident that Internet control is
a powerful force for governments to wield. Whether or not AS-level topology supports these efforts is a research question pivotal to
an understanding of the dynamics of Internet censorship and surveillance.

%Diverse Censorship Architecture
\par
Every nation has a different layout and count of ASes. The censorship and surveillance strategies of nations also differ. For instance,
China both conducts keyword filtering in border ASes and in internal provincial nodes \cite{chinafiltering}. Another nation that conducts
extensive Internet censorship, Iran, has been found to route all of its Internet traffic through a centralized facility \cite{irancensor}.
Having views into the AS topology of a nation, then, will both help researchers identify nations that could easily conduct censorship and
also provide possible insight into what kind of censorship is likely being conducted. The measure of chokepoint potential, defined later in this paper,
is an effective way to capture the important properties of border ASes related to these capabilities.

>>>>

\par Widespread Internet censorship and surveillance pose a
significant threat to individuals throughout the world. As routine
tasks, communications, entertainment, and information move on-line and
are mediated by the Internet, most of us have little choice about
whether or not to rely on the Internet.  According to the
International Telecommunication Union (ITU), the number of individual
Internet users increased from 1.024 million in 2005 to 3.578 million
in 2017 \cite{itu}. The majority of these users operate in an
environment that restricts Internet freedom in some way. For example,
the 2017 Freedom on the Net report from Freedom House reports that
64\% of Internet users belong to a nation with Internet that is not
free or partly free \cite{FOTN}.  Beyond censorship and surveillance,
the EU is considering content rules surrounding copyright, net
neutrality rules in the U.S. were recently overturned, and large
content delivery networks are under enormous pressure to 'do
something' about fake news and bad actors. Taken together, these
trends will likely restructure the Internet in unforeseen ways,
as organizations respond to new challenges and realities.

Today, most such control is exercised at the country level,
as governments have recognized both the threat and the opportunity
that is posed by ubiquitous on-line communication. For example, much
of the organization, revolutionary momentum, and broadcasting of
events during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and similarly several countries
sought to control these movements by disconnecting in-country networks from the rest of the world (FIXME: need references here).

These two factors, increasing levels of content monitoring and
Internet dependence, point to the need for improved tools and methods
for studying worldwide Internet censorship and surveillance over time.
[A SENTENC OR TWO HERE SUMMARIZING THE STATE OF THE FIELD AND WHAT'S
  MISSING.]  In this paper, we focus on AS-level topology and on
censorship, asking how AS topology has changed over time with respect
to national boundaries.  We define \emph{chokepoint potential} to
quantify how a country’s AS topology is organized in terms of paths
that can carry traffic across international borders.  We developed a
suite of tools, called \toolname, for studying national chokepoints on
the AS graph efficiently. To illustrate these ideas and tools, we
study how chokepoint potential correlates with two independent
measures of civilian liberty, finding [NEED A RESULT HERE]. [NEED A
  RESULT FOR WHAT WE FOUND FOR EVOLU- TION OVER TIME].

The paper extends earlier research on AS topology, first by introducing the chokepoint potential measure, then by presenting open-source cross-platform tools for simulating
and Border Gateway Protocol (BGP) networks, determining chokepoint potential at the country level, and analyzing how this measure has changed over time for certain countries of interest.

%Whether or not AS-level topology supports
%these efforts is a research question pivotal to an understanding of
%the dynamics of Internet censorship and surveillance.

%% \par
%% The Internet has been used as a tool for the citizens of authoritarian nations to voice opinions,
%% organize revolutionary movements, and connect with other nations' governments and citizens
%% to seek aid. Much of the organization, revolutionary momentum, and broadcasting
%% of happenings during the Arab Spring can be attributed to social media communications
%% through the Internet \cite{arabspring}. Because of this potential, national governments may
%% take interest in maximizing their ability to control the flow of information on the Internet.
%Censorship and Surveillance are growing phenomena

%The Internet is Dynamic and growing

We are interested in how AS topologies have changed as the total size of the graph has grown from about 10,000 nodes in the early 2000s to over 60,000 today.
The structural
properties of national AS graphs have evolved differently
from nation to nation whether from economic decision making, infrastructural necessities, or
efforts to build a powerful censorship and surveillance
network.
%The Autonomous Systems (AS) layer of the Internet has grown and changed dramatically over its history.
%The locations and relationships of these ASes determine how many chokepoints
%of AS-level routing exist and what strength these chokepoints have in regards to paths intercepted.
This rapid expansion, together with the changing role of national
governments, points to the importance of understanding properties like
path robustness, AS hierarchies, and the potential for organizations to
control information as it flows in and out of their networks.

%Current Events

%Diverse Censorship Architecture
\par Every nation has a different layout and count of ASes. The
censorship and surveillance strategies of nations also differ. For
instance, China both conducts keyword filtering in border ASes and in
internal provincial nodes \cite{chinafiltering}, while Iran routes its
Internet traffic through a centralized facility \cite{irancensor}.
Having views into the AS topology of a nation, then, will both help
researchers identify nations that could easily conduct censorship and
also provide possible insight into what kind of censorship is likely
being conducted. The measure of chokepoint potential, defined later in
this paper, is a succint way to estimate the important properties of
border ASes related to these capabilities.
